Looking for CDI Bias: WG Comprehension

### 2021-07-16 02-preliminary-WGcomp.Rmd
fitted SES DIF model

@@

>>>>

table(d_demo$mom_ed)
# high SES = mom_ed >= Some College (739 high, 324 low-SES)
d_demo <- d_demo %>% mutate(ses_group = ifelse(as.numeric(mom_ed)>4, "high", "low"))

@@

## DIF Model: SES

```{r, eval=F}
ses_group = as.character(d_demo$ses_group)

#mg1 <- multipleGroup(d_mat, 1, group = ses_group, SE = T) 
mg2 <- multipleGroup(d_mat, model = 1, group = ses_group, technical=list(NCYCLES=4000), 
                     invariance = 'slopes', verbose = T)

m_sc2 <- multipleGroup(d_mat, 1, group = ses_group, technical=list(NCYCLES=2000),
                       invariance=c('slopes', 'intercepts', 'free_var','free_means'))
mod_sc1 <- multipleGroup(d_mat, 1, group = ses_group, technical=list(NCYCLES=2000), #fixed means
                             invariance=c('slopes', 'intercepts', 'free_var'))
mod_fullconstrain <- multipleGroup(d_mat, 1, group = ses_group, technical=list(NCYCLES=2000),
                             invariance=c('slopes', 'intercepts'))

#extract.group(m_sc2, "high")
#extract.group(m_sc2, "low")

save(file = here("data/eng_wg_comp_SES_DIF.Rds"), 
     mg2, m_sc2, mod_sc1, mod_fullconstrain)
```
